Peer-to-Peer Permissionless Consensus via Reputation

### 2023-08-14 freechains/rebuttal.md

We would like to thank the reviewers for the thoughtful comments, questions,
and criticism.

We accommodate all clarifications and answers in the final version of the
paper.

The link that follows shows the *diff* to reach the final version:

- \url{https://github.com/fsantanna-no/sbseg-23/compare/0145ec9d59ff2e1b4e1053505bf5614d63326166..b51a401cb67ece6857bd697f39df0ea428b0ba07?diff=split}

@@

> Além disso, é possível que um usuário malicioso participe de mais de uma
> cadeia em um fork? neste caso como fica a regra de merge? e se der empate,
> todos devem escolher o mesmo fork para começar, como isso seria feito?

A reputação de um usuário em uma cadeia X não é válida em uma cadeia Y.
Portanto, interpretamos o comentário acima como "...participe de mais de um
fork em uma mesma cadeia".

Sim, se o usuário malicioso dispor de 1 rep, ele pode escrever propositalmente
em vários forks.
Nesse caso, a reputação prévia dele vai contar igualmente em todos os merges,
se anulando e, portanto, não influenciando no resultado final do merge.

Em caso de empate, que pode acontecer mesmo sem usuários maliciosos, o hash do
fork será o critério considerado por todos igualmente.
Esse critério é descrito no final da Seção 2.2:

@@

# Reviewer 2

> It is strange that known techniques like EigenTrust are not even mentioned,
> even though we are in the blockchain domain.

We added a new paragraph at the end of Section 4 (Related Work), as follows:

> Some works for P2P file sharing propose to account the reputation of peers to
> form a web of trust based on their behavior
> history [Wang,EigenTrust].
> However, there are three key aspects in terms of scope that distinguishes our
> reputation system: its focus on the contents, its subjective nature, and its
> dependency on consensus.
> First, it is the actual contents that are stored and evaluated in the forums,
> with the identities being a secondary attribute.
> Second, content evaluation is subjective, as well as any decision to revoke
> posts or to fork forums.
> Third, at any given point in time, peers must agree on a common forum DAG
> prefix with global and deterministic accuracy to act identically as a whole.
> In this case, consensus is fundamental, since a subtle off-by-one discrepancy
> in reputation creates an irreconcilable fork in the network.
> Achieving consensus on a permissionless network is the key contribution of this
> work.
